---
title: "Journal (reproducible report)"
author: "Nilesh Hampiholi"
date: "2020-11-05"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# Challenge 1 :  Introduction to Tidyverse 

Last compiled: `r Sys.Date()`

## Analyze the sales by location 

## Analyze the sales by location and year

```{r plot, fig.width =14 , fig.height= 7}
#import libraries
library(tidyverse)
library(readxl)
library(lubridate)
#load files
bikes_tbl      <- read_excel ("D:/pADHAI/SEM_3/DataScience/DS_101/00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel ("D:/pADHAI/SEM_3/DataScience/DS_101/00_data/01_bike_sales/01_raw_data/orderlines.xlsx" )
bikeshops_tbl  <- read_excel("D:/pADHAI/SEM_3/DataScience/DS_101/00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")

 #examine files

 #join files using the keys product id, bikeshop id and customer id
bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))

#Examine the joined files 

# Select State as feature and examine the data 

# wrangle data 
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  separate(col    = location,
           into   = c("city","state"),
           sep    = ",") %>%
  mutate(total.price = price * quantity) %>%
  select(-...1, -gender) %>%
  select(-ends_with(".id")) %>%
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  
  select(order.id, contains("order"), contains("model"), contains("city"),state,
         price, quantity, total.price,
         everything()) %>%
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))

#extract required column
sales_by_year_tbl <- bike_orderlines_wrangled_tbl %>%
  select(order_date, total_price) %>%
  mutate(year = year(order_date)) %>%
  group_by(year) %>% 
  summarize(sales = sum(total_price)) %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = "€"))



#plot bar chart
sales_by_year_tbl %>%
  
  # Setup canvas with the columns year (x-axis) and sales (y-axis)
  ggplot(aes(x = year, y = sales)) +
  
  # Geometries
  geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
  geom_label(aes(label = sales_text)) + # Adding labels to the bars
  geom_smooth(method = "lm", se = FALSE) + # Adding a trendline
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = "€")) +
  labs(
    title    = "Revenue by year",
    subtitle = "Upward Trend",
    x = "", # Override defaults for x and y
    y = "Revenue"
  )


sales_by_year_state_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns and add a year
  select(order_date, total_price, state) %>%
  mutate(year = year(order_date)) %>%
  
  # Group by and summarize year and main catgegory
  group_by(year, state) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  
  # Format $ Text
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = "€"))

#plot by year and locATION 
head(sales_by_year_state_tbl,10)


sales_by_year_state_tbl %>%

  ggplot(aes(x = year, y = sales, fill = state)) +
  geom_col() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) +

  facet_wrap(~ state, scales = "free_y") +
  
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = "€")) +
  labs(
    title = "Revenue by year and state",
    subtitle = "Each product category has an upward trend",
    fill = "State" # Changes the legend name
  )


library("writexl")
bike_orderlines_wrangled_tbl %>%
  write_xlsx("D:/pADHAI/SEM_3/DataScience/DS_101/00_data/01_bike_sales/bike_orderlines.xlsx")
# 7.2 CSV ----
bike_orderlines_wrangled_tbl %>% 
  write_csv("D:/pADHAI/SEM_3/DataScience/DS_101/00_data/01_bike_sales/bike_orderlines.csv")


# 7.3 RDS ----

bike_orderlines_wrangled_tbl %>% 
  write_rds("D:/pADHAI/SEM_3/DataScience/DS_101/00_data/01_bike_sales/bike_orderlines.rds")

```

# Challenge 2 : Data Acquisition

Last compiled: `r Sys.Date()`

## API Challenge

```{r}
library(glue)
library(httr)
library(jsonlite)
resp <- GET("http://api.open-notify.org/iss-pass.json", query = list(lat =53.5511, lon = 9.9937))
resp
data = fromJSON(rawToChar(resp$content))
data

```

## Comparing Compititor Data
```{r}
# WEBSCRAPING ----


# 1.0 LIBRARIES ----

library(tidyverse) # Main Package - Loads dplyr, purrr, etc.
library(rvest)     # HTML Hacking & Web Scraping
library(xopen)     # Quickly opening URLs
library(jsonlite)  # converts JSON files to R objects
library(glue)      # concatenate strings
library(stringi)   # character string/text processing

# 1.1 COLLECT PRODUCT TYPES ----
url_home          <- "https://www.radon-bikes.de/"
#xopen(url_home)
html_home         <- read_html(url_home)
bike_family_tbl <- html_home %>%
html_nodes(css = ".megamenu__item > a") %>%  
html_attr('href') %>%  
discard(.p = ~stringr::str_detect(.x,"wear")) %>%  
enframe(name = "position", value = "cat_subcat_url") %>%  
  
mutate(family_id = str_glue("https://www.radon-bikes.de{cat_subcat_url}bikegrid"))
#bike_family_tbl

 
# 2.0 COLLECT BIKE DATA ----

bike_category_url <- bike_family_tbl$family_id[1]
#xopen(bike_category_url)
html_bike_category  <- read_html(bike_category_url)

bike_name_tbl        <- html_bike_category %>%
html_nodes(css = ".m-bikegrid__info .a-heading--small") %>%
html_text() %>%


enframe(name = "position", value = "name")
#bike_name_tbl 

bike_price_tbl <- html_bike_category %>%
html_nodes(css = ".m-bikegrid__price.currency_eur .m-bikegrid__price--active") %>%  
html_text() %>% 
enframe(name = "position", value = "price")
#bike_price_tbl

model_price_tbl <- left_join(bike_name_tbl, bike_price_tbl)%>% 
select(name, price)
head(model_price_tbl,10)

```






# Challenge 3 : Data Wrangling 

## 1. Patent Dominance
So far this is just a blog where you can write in plain text and serve your writing to a webpage. One of the main purposes of this lab journal is to record your progress learning R. The reason I am asking you to use this process is because you can both make a website, and a lab journal, and learn R all in R-studio. This makes everything really convenient and in the same place. 
## 2.Recent patent acitivity
So, let's say you are learning how to make a histogram in R. For example, maybe you want to sample 100 numbers from a normal distribution with mean = 0, and standard deviation = 1, and then you want to plot a histogram. You can do this right here by using an r code block, like this:

```{r}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```
#Challenge 4 : 

## 1. Map the time course of the cumulative Covid-19 cases
When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag) from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You'll learn that all of these things and more can be customized in each R code block.
## 2.  Visualize the distribution of the mortality rate (deaths / population)


